---
title: "Applied Econometrics using ArcGIS"
author: "Aziz"
date: '2022-08-03'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(here)
library(readxl)
library(tidyverse)
library(dplyr)
library(fixest)
library(modelsummary)
library(stats)
library(stringr)
library(ggplot2)
```



```{r cars}

here::i_am("paper_replication.Rmd")
dir_data    <- here("../data")

```




```{r}
filename <- "housingbenefitreceivers.xls"

### Import ***xls data

    housBen <- read_excel( paste( dir_data, filename, collapse = " + ", sep = "/" ))
    colnames(housBen)[5:12]<-c(2013:2019)

    housBen <- housBen[, c('Kennziffer', 'Raumeinheit', '2016', '2017')]%>%
      mutate(
        change_housBenefit <- as.numeric(housBen$`2017`) - as.numeric(housBen$`2016`)) %>%
      select(-c(3,4))
    
    colnames(housBen)[3] <- 'chng_housBenefit'
    housBen <- housBen[-1,]

```




```{r pressure, echo=FALSE}

filename <- "asylum_seekers_people.xls"

### Import ***xls data

    asylum_seekers <- read_excel( paste( dir_data, filename, collapse = " + ", sep = "/"))
    colnames(asylum_seekers)[4:11]<-c(2012:2019)
    asylum_seekers <- select(asylum_seekers, c(1,7))%>%
      mutate(
        asylum_seekers$`2015` <- as.numeric(asylum_seekers$`2015`) * 100000 / 100
      )
    asylum_seekers <- asylum_seekers[-1,-2]
    colnames(asylum_seekers)[2] <- 'asySeekers_2015'

    
    kreis<- left_join(housBen, asylum_seekers, by="Kennziffer")
```




```{r pressure, echo=FALSE}

filename <- "0-25.2016.xls"

### Import ***xls data

    temp0_25_2016 <- read_excel( paste( dir_data, filename, collapse = " + ", sep = "/"))
    temp0_25_2016 <- mutate(temp0_25_2016,
        total_under25_2016 <- as.numeric(temp0_25_2016$`Einwohner unter 6 Jahre`) + 
          as.numeric(temp0_25_2016$`Einwohner von 6 bis unter 18 Jahren`) + 
          as.numeric(temp0_25_2016$`Einwohner von 18 bis unter 25 Jahren`))%>%
      select(1,2,7)
    temp0_25_2016 <- temp0_25_2016[-1,]
    colnames(temp0_25_2016)[3] <- 'under25_2016'
    
filename <- "0-25.2017.xls"

### Import ***xls data

    temp0_25_2017 <- read_excel( paste( dir_data, filename, collapse = " + ", sep = "/"))
    temp0_25_2017<-mutate(temp0_25_2017,
      total_under25_2017 <- as.numeric(temp0_25_2017$`Einwohner unter 6 Jahre`) + 
                              as.numeric(temp0_25_2017$`Einwohner von 6 bis unter 18 Jahren`) + 
                              as.numeric(temp0_25_2017$`Einwohner von 18 bis unter 25 Jahren`))%>%
      select(1,7)
    temp0_25_2017 <- temp0_25_2017[-1,]
    colnames(temp0_25_2017)[2] <- 'under25_2017'

youth <- left_join(temp0_25_2016, temp0_25_2017, by='Kennziffer')
    
    

filename <- "25-65.2016.xls"

### Import ***xls data

    temp25_65_2016 <- read_excel( paste( dir_data, filename, collapse = " + ", sep = "/"))
    temp25_65_2016<-mutate(temp25_65_2016,
      total_25_65_2016 <- as.numeric(temp25_65_2016$`Einwohner von 25 bis unter 30 Jahren`) + 
                              as.numeric(temp25_65_2016$`Einwohner von 30 bis unter 50 Jahren`) + 
                              as.numeric(temp25_65_2016$`Einwohner von 50 bis unter 65 Jahren`))%>%
      select(1,7)
    temp25_65_2016 <- temp25_65_2016[-1,]
    colnames(temp25_65_2016)[2] <- '25_65_2016'


youth <- left_join(youth, temp25_65_2016, by='Kennziffer')
    
    
filename <- "25-65.2017.xls"

### Import ***xls data

    temp25_65_2017 <- read_excel( paste( dir_data, filename, collapse = " + ", sep = "/"))
    temp25_65_2017<-mutate(temp25_65_2017,
      total_25_65_2017 <- as.numeric(temp25_65_2017$`Einwohner von 25 bis unter 30 Jahren`) + 
                              as.numeric(temp25_65_2017$`Einwohner von 30 bis unter 50 Jahren`) + 
                              as.numeric(temp25_65_2017$`Einwohner von 50 bis unter 65 Jahren`))%>%
      select(1,7)
    temp25_65_2017 <- temp25_65_2017[-1,]
    colnames(temp25_65_2017)[2] <- '25_65_2017'


youth <- left_join(youth, temp25_65_2017, by='Kennziffer')
    

youth <- mutate(youth,
                chng_youth <- round(under25_2017 / youth$`25_65_2017` - under25_2016 / youth$`25_65_2016`, 4))%>%
  select(1,7)
colnames(youth)[2] <- 'chng_youth'

kreis <- left_join(kreis, youth, by='Kennziffer')

```






```{r pressure, echo=FALSE}

filename <- "foreigners_share.xls"

### Import ***xls data

    for_share <- read_excel( paste( dir_data, filename, collapse = " + ", sep = "/"))
    colnames(for_share)[4:11]<-c(2012:2019)
    
    for_share <- for_share[, c('Kennziffer', 'Raumeinheit', '2016', '2017')]%>%
      mutate(
        change_shareFor <- as.numeric(for_share$`2017`) - as.numeric(for_share$`2016`)) %>%
      select(-c(2:4))
    
    colnames(for_share)[2] <- 'chng_shareFor'
    for_share <- for_share[-1,]

    
    kreis<- left_join(kreis, for_share, by="Kennziffer")
```




```{r pressure, echo=FALSE}

filename <- "gdp_percap.xls"

### Import ***xls data

    gdp <- read_excel( paste( dir_data, filename, collapse = " + ", sep = "/"))
    colnames(gdp)[4:11]<-c(2012:2019)
    
    gdp <- gdp[, c('Kennziffer', 'Raumeinheit', '2016', '2017')]%>%
      mutate(
        change_GDPpercap <- round(log(as.numeric(gdp$`2017`)*1000) - log(as.numeric(gdp$`2016`)*1000),4)) %>%
      select(-c(2:4))
    
    colnames(gdp)[2] <- 'chng_logGDPpercap'
    gdp <- gdp[-1,]

    
    kreis<- left_join(kreis, gdp, by="Kennziffer")
```



```{r pressure, echo=FALSE}

filename <- "shareFemale.xls"

### Import ***xls data

    popmale <- read_excel( paste( dir_data, filename, collapse = " + ", sep = "/"))
    colnames(popmale)[4:11]<-c(2012:2019)
    
    popmale <- popmale[, c('Kennziffer', 'Raumeinheit', '2016', '2017')]%>%
      mutate(
        shareMale2016 <- 100 - as.numeric(popmale$`2016`),
        shareMale2017 <- 100 - as.numeric(popmale$`2017`),
        change_shareMale <- shareMale2017 - shareMale2016) %>%
      select(-c(2:6))
    
    colnames(popmale)[2] <- 'chng_shareMale'
    popmale <- popmale[-1,]


    kreis<- left_join(kreis, popmale, by="Kennziffer")

```



```{r pressure, echo=FALSE}

filename <- "unemployment_rate.xls"

### Import ***xls data

    unempl <- read_excel( paste( dir_data, filename, collapse = " + ", sep = "/"))
    colnames(unempl)[4:11]<-c(2012:2019)
    
    
    unempl <- unempl[, c('Kennziffer', 'Raumeinheit', '2016', '2017')]%>%
      mutate(
        change_unempl <- as.numeric(unempl$`2017`) - as.numeric(unempl$`2016`)) %>%
      select(-c(2:4))
    
    colnames(unempl)[2] <- 'chng_unempl'
    unempl <- unempl[-1,]

    
    kreis<- left_join(kreis, unempl, by="Kennziffer")

```




```{r pressure, echo=FALSE}

filename <- "foreign_unemployed.xls"

### Import ***xls data

    for_unempl <- read_excel( paste( dir_data, filename, collapse = " + ", sep = "/"))
    colnames(for_unempl)[4:11]<-c(2012:2019)
    
    
    for_unempl <- for_unempl[, c('Kennziffer', 'Raumeinheit', '2016', '2017')]%>%
      mutate(
        change_for_unempl <- as.numeric(for_unempl$`2017`) - as.numeric(for_unempl$`2016`),
        for_unempl_2017 <- as.numeric(for_unempl$`2017`)) %>%
      select(-c(2:4))
    
    colnames(for_unempl)[2:3] <- c('chng_for_unempl', 'for_unempl_2017')
    for_unempl <- for_unempl[-1,]

    
    kreis<- left_join(kreis, for_unempl, by="Kennziffer")

```



Data about EAEs capacities of each state is obtained from the original paper

```{r}

bundeslands <- c("Baden-Wuertemberg", "Bavaria", "Berlin", "Brandenburg", "Bremen", "Hamburg", "Hesse", 
                  "Mecklenburg Western Pomerania", "Lower Saxony", "North Rhine-Westphalia (NRW)", 
                  "Rhineland Palatinate", "Saarland", "Saxony", "Saxony-Anhalt", "Schleswig-Holstein",
                  "Thuringia")
capacities <- c(26400, 22377, NA, 5092, NA, NA, 22047, 989, 5028, 16245, 10622, 1300, 16845, 6259,
                15667, 6951)
id <- c(8, 9, 11, 12, 4, 2, 6, 13, 3, 5, 7, 10, 14, 15, 1, 16)

eae_capacity <- cbind(id, bundeslands, capacities)%>%
  as.data.frame()
eae_capacity$id <- as.numeric(eae_capacity$id)
eae_capacity$capacities <- as.numeric(eae_capacity$capacities)
eae_capacity <- arrange(eae_capacity, id)

```




EAEs

here, average capacity of states is assigned to its counties


```{r}

eae <- kreis[,1:2] %>%
  mutate(state_id=substring(Kennziffer,1,2))   # here first 2 numbers of Kennziffer is extracted
eae$state_id <- as.numeric(eae$state_id)

# here i counted how many counties each state has

counties <- c()

for (i in 1:16){
  number <- nrow(eae[eae$state_id==i,])
  counties <- append(counties, number)
}

# here i am joining counties to eae_capacity

eae_capacity <- cbind(eae_capacity, counties) 
eae_capacity$average <- round(eae_capacity$capacities / eae_capacity$counties)

# here each county receives average eae_capacity of its state

eae <- cbind(eae, average_eae=c(NA*nrow(eae)))

for (i in 1:16) {
  for (k in 1:nrow(eae)){
    if (eae$state_id[k]==i) {
      eae[k, "average_eae"] <- eae_capacity[i, "average"]
    }
  }

}


filename <- "poptotal.xls"

### Import ***xls data

    poptotal <- read_excel( paste( dir_data, filename, collapse = " + ", sep = "/"))
    colnames(poptotal)[4:11]<-c(2012:2019)
    poptotal <- select(poptotal, c(1,7)) %>%
      mutate(
        pop2015 <- as.numeric(poptotal$`2015`)
      )
    poptotal <- poptotal[-1,-2]
    colnames(poptotal)[2] <- 'pop2015'    

    #here EAE capacities are calculated per 100.000 people in each state
            
    eae <- left_join(eae, poptotal, by='Kennziffer')
    eae$eae <- round(eae$average_eae / eae$pop2015 * 100000)
    eae <- select(eae, c(1,3,6))
    
    kreis<- left_join(kreis, eae, by="Kennziffer")

```



Here, TOP 5% GDP per capita generating counties are identified



```{r pressure, echo=FALSE}

filename <- "gdp_percap.xls"

### Import ***xls data

    gdp_rank <- read_excel( paste( dir_data, filename, collapse = " + ", sep = "/"))
    colnames(gdp_rank)[4:11]<-c(2012:2019)
    
    
    
    gdp_rank <- gdp_rank[, c('Kennziffer', 'Raumeinheit', '2016')]%>%
      mutate(
        gdp2016 <- as.numeric(gdp_rank$`2016`)
      )
    colnames(gdp_rank)[4] <- 'gdp2016'

    gdp_rank <- gdp_rank[-1,-3] %>%
            arrange(desc(gdp2016))
    
    threshold <- quantile(gdp_rank$gdp2016, probs=c(0.95))      # threshold GDP value for counties to be on a list of TOP 5%
    counties_rank <- gdp_rank$Raumeinheit[gdp_rank$gdp2016 >= threshold ]

    
```
```{r}

for (i in 1:length(counties_rank)) {
  if (str_sub(counties_rank[i], -5)=='Stadt'){
    counties_rank[i] <- substr(counties_rank[i], start = 1, stop = nchar(counties_rank[i])-7)
  } else {
    next
  }
}

counties_rank

```


Here, a new column is introduced to the main dataset, which can take a value of 2 if the corresponding county is on the list of TOP 5% GDP per capita producing counties, a value of 1 if the corresponding county is a neighbour to the TOP 5% counties, otherwise 0.


```{r}

kreis$county_rank <- c(rep(0, times = nrow(kreis)))

for (i in 1:nrow(kreis)){
  if (kreis$Raumeinheit[i] %in% counties_rank){
    kreis$county_rank[i] = 2
  }
}


```


Here, neighbours data is obtained by German counties shape file by applying ArcGIS tools in Python


```{r}

filename <- "neighbours.xls"

### Import ***xls data
    neighbours <- read_excel( paste( dir_data, filename, collapse = " + ", sep = "/"))%>%
      select(c(1:3))
    neighbours <- neighbours[neighbours$src_NAME_2 %in% counties_rank,]


    counties_near <- c(unique(neighbours$nbr_NAME_2))
    
    for (i in 1:nrow(kreis)) {
      if (kreis$Raumeinheit[i] %in% counties_near){
        kreis$county_rank[i] <- 1
      } else{
        next
      }
    }

kreis$county_rank <- as.factor(kreis$county_rank)
    
```




NOW IT IS TIME TO MAKE A REGRESSION


```{r}

# First-differnece model with a dependent variable of total unemployment rate

model1 <- lm(chng_unempl ~ asySeekers_2015 + eae + 
                  chng_logGDPpercap + chng_youth + chng_shareMale + 
                  chng_shareFor + chng_housBenefit, data = kreis)


# First-differnece model with a dependent variable of non-Germans unemployment rate

model2 <- lm(chng_for_unempl ~ asySeekers_2015 + eae + 
                  chng_logGDPpercap + chng_youth + chng_shareMale + 
                  chng_shareFor + chng_housBenefit, data = kreis)


# Logistic model with a dependent variable of non-Germans unemployment rate


kreis$new_for_unempl_2017 <- kreis$for_unempl_2017 / 100


model3 <- glm(new_for_unempl_2017 ~ asySeekers_2015 + eae + 
                  chng_logGDPpercap + chng_youth + chng_shareMale + 
                  chng_shareFor + chng_housBenefit, data = kreis, family = 'binomial')


# First-differnece model with a dependent variable of non-Germans unemployment rate plus a independent dummy variable

model4 <- feols(chng_for_unempl ~ asySeekers_2015 + eae + 
                  chng_logGDPpercap + chng_youth + chng_shareMale + 
                  chng_shareFor + chng_housBenefit + county_rank, data = kreis)



models <- list('OLS (overall)'= model1, 
               'OLS (non-German)' = model2, 
               'Logit (non-German)' = model3, 
               'OLS (non-German +  TOP5% counties)' = model4)


# changing the name of variables in modelsummary

cm <- c('asySeekers_2015' = "Inflow of asylum seekers (2015)",
        'eae' = "EAE capacity",
        "chng_logGDPpercap" = "Change in Log GDP per capita",
        "chng_youth" = "Change in youth share",
        "chng_shareMale" = "Change in male share",
        "chng_shareFor" = "Change in foreigner's share",
        "chng_housBenefit" = "Change in House Benefit receivers",
        "county_rank1" = "Neighbour counties",
        "county_rank2" = "TOP 5% counties")



modelsummary(models, fmt = 5, stars = T,  gof_omit = "AIC|BIC|RMSE|F|Log.Lik.", coef_map = cm, title = "Replication")



```


Plot of logistic model with an arbitrary dataset


```{r}

newdata_check = expand.grid(asySeekers_2015=seq(0,45000, length.out=50), eae = 150, chng_logGDPpercap = median(kreis$chng_logGDPpercap), chng_youth = median(kreis$chng_youth), chng_shareMale = median(kreis$chng_shareMale), chng_shareFor = median(kreis$chng_shareFor),  chng_housBenefit=median(kreis$chng_housBenefit), county_rank = 0:2)

newdata_check$y <- predict(model3, newdata = newdata_check, type = 'response')

ggplot(newdata_check, aes(asySeekers_2015, y)) +
  geom_line(color='red')+
  ggtitle("Plot of logistic model")+
  xlab("Number of asylum seekers")+
  ylab("Expected unemployment rate")+theme(
  plot.title = element_text(color="red", size=14, face="bold.italic"),
  axis.title.x = element_text(color="blue", size=14, face="bold"),
  axis.title.y = element_text(color="#993333", size=14, face="bold"))

```

